\documentclass[11pt,a4paper,]{moderncv}
\moderncvstyle{casual} % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'

\definecolor{color0}{rgb}{0,0,0}% black
\definecolor{color1}{HTML}{A52A2A}% custom
\definecolor{color2}{rgb}{0.45,0.45,0.45}% dark grey

\usepackage[scaled=0.86]{DejaVuSansMono}
\usepackage{ragged2e}
\usepackage{comment}
\usepackage{xcolor}
\definecolor{linkblue}{HTML}{1A4D8F} % Muted dark blue, adjust as needed
\usepackage[colorlinks=true, urlcolor=linkblue, linkcolor=black]{hyperref}

\providecommand{\tightlist}{
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}
}
\def\donothing#1{#1}
\def\emaillink#1{#1}

% adjust the page margins
\usepackage[a4paper,scale=0.75,footskip=60pt,bottom=1in,left=0.75in,right=0.75in,top=1in]{geometry}
\setlength{\hintscolumnwidth}{2cm} % if you want to change the width of the column with the dates

% personal data
\name{Nikhil}{Vidhani}
\title{\Large Lead Data Scientist -- Digital Fulfilment \& Simulations, Target Corporation}
\phone[mobile]{+91-994-567-3757}
\email{\donothing{\href{mailto:nikhil141088@gmail.com}{\nolinkurl{nikhil141088@gmail.com}}}}
\social[linkedin]{nikhil-vidhani}
\social[github]{nik141088}
% \photo[70pt][0.4pt]{nikhil-wns-pic.jpg} % commented out for cleaner, less-biased CV

% main content
\begin{document}
\makecvtitle

\newenvironment{smallblockquote}{
  \par
  \medskip
  \leftskip=2em\rightskip=0em
  \noindent\ignorespaces
  }{\par\medskip}

\newenvironment{blockquote}{
  \par
  \medskip
  \leftskip=4em\rightskip=0em
  \noindent\ignorespaces
  }{\par\medskip}

\hypertarget{executive-summary}{
\section{Executive Summary}\label{executive-summary}}

\begingroup
  \par
  \medskip
  \leftskip=4em\rightskip=0em
  \noindent\ignorespaces

\begin{itemize}
    \item Architected end-to-end simulation capabilities for order allocation and available-to-promise (ATP) systems impacting 3\% of all digital sales (\$600+Mn).
    \item Ideated, designed and implemented a new consolidation algorithm for ATP projected to save \$20Mn+ in shipping costs and drive \$300Mn+ in incremental sales.
    \item Built unified simulation and ATP tools that are now the primary platform for scenario testing, sensitivity analysis, and policy design across Target's digital fulfilment network.
    \item Deep technical expertise in Python and R with extensive experience in distributed data pipelines (Spark, Kafka, Hive/Hadoop/SQL) algorithm design, machine learning, software engineering, and data pipeline development.
    \item Cross-functional leader partnering with product, engineering, and operations to translate ambiguous business problems into experiment-ready use cases, mentoring a 6-member data science team and driving an experimentation culture.
    \item Prior experience leading a data science team at WNS on finance and auditing analytics, and a strong research foundation with a Ph.D. in Finance (IIM Bangalore) and Master's in Engineering (IISc Bangalore) with work presented at multiple conferences.
\end{itemize}

  \par\medskip
\endgroup

\hypertarget{industry-and-research-experience}{
\section{Industry and Research
Experience}\label{industry-and-research-experience}}

\nopagebreak
    \cventry{\parbox[t]{2cm}{\raggedright Nov~2022 -- \newline Present}}
    {Lead Data Scientist}{Target Corporation, Bangalore}{}{Team Size: 5}{
    \begin{itemize}
        \item Own design and expansion of end-to-end last-mile simulation platforms (digital twin) for order allocation and available-to-promise, enabling network-wide what-if analysis on inventory, capacity, and promise policies.
        \item Develop and manage advanced cost-versus-speed optimisation models for consolidation and promise speed generation, using large-scale simulations and production data to identify trade-offs and drive multi-million-dollar improvements in ship cost and digital sales.
        \item Lead product and technical roadmap for multiple simulation tools, including requirements prioritisation, code and design reviews, release planning, and operational support.
        \item Partner with supply chain, fulfilment, and digital product teams to scope high-impact questions, run scenario and sensitivity analyses, and recommend data-driven policy changes for speed, cost, and conversion.
        \item Collaborate closely with engineering to productionise next-generation promise logic and data pipelines (Kafka-based ingestion, PySpark/Hive transforms), providing design docs, test plans, and knowledge-transfer sessions.
        \item Mentor a team of five senior and junior data scientists through 1:1s, design discussions, and sprint ceremonies, coaching them on experimentation, stakeholder communication, and engineering best practices.
    \end{itemize}
    }
    \cventry{\parbox[t]{2cm}{\raggedright Feb~2022 -- \newline Nov~2022}}
    {Sr. Group Manager (Data Science)}{WNS Global Services, Bangalore}{}{Team Size: 6}{
    \begin{itemize}
        \item Led a 6-member data science team delivering analytics and machine-learning solutions for finance and accounting use cases (payments, collections, reporting, prediction, and auditing) for global clients, driving multi-million-dollar operational savings.
        \item Owned end-to-end lifecycle from problem framing with business stakeholders through data engineering, modelling, API development, and automated deployment, ensuring solutions were reliable and maintainable.
        \item Maintained shared GitHub repositories, code quality standards, and CI/CD workflows; mentored junior team members through code reviews, technical sessions, and structured knowledge-sharing.
    \end{itemize}
    }
    \cventry{\parbox[t]{2cm}{\raggedright Jun~2016 -- \newline Jan~2022}}
    {Research Scholar}{Indian Institute of Management, Bangalore}{}{IC}{
    \begin{itemize}
        \item Extensively researched asset pricing anomalies, examined impact of disagreement on trading volume, analyst forecasts, and 10K document characteristics
        \item Undertook comprehensive data collection, cleaning, modelling, and statistical analysis
        \item Published multiple papers and presented in several conferences. \textit{Complete list available at:} 
\href{https://github.com/nik141088/CV/blob/main/publications_CV.pdf}{\texttt{publications\_CV.pdf}}
    \end{itemize}
    }
    \cventry{\parbox[t]{2cm}{\raggedright Jun~2018 -- \newline Jan~2022}}
    {Primary Instructor}{Programming and Data Analysis}{}{Batch Size: 5-40}{
    \begin{itemize}
        \item Took multiple short/long courses on R programming, data analysis, and LaTeX
        \item Instructor Rating: 4.7/5 (\href{https://github.com/nik141088/applied-R}{https://github.com/nik141088/applied-R})
    \end{itemize}
    }
    \cventry{\parbox[t]{2cm}{\raggedright Jul~2012 -- \newline May~2016}}
    {Software Engineer}{Cisco Systems, Bangalore}{}{IC}{
    \begin{itemize}
        \item Design, implement, test, review, and documentation of 4G-LTE and WiFi systems
        \item High Availability/Redundancy architecture. Network security.
    \end{itemize}
    }

% \pagebreak

\hypertarget{major-projects}{
\section{Major Projects}\label{major-projects}}

\nopagebreak
    \cventry{\parbox[t]{2cm}{\raggedright 2025 -- \newline Present}}
    {Consolidation Algorithm Revamp}{Target}{}{}{
    \begin{itemize}
        \item Redesigned Target's consolidation algorithm to jointly optimise customer promise speed and shipping cost across the last-mile network, replacing legacy heuristics with a principled modelling framework.
        \item Used integrated simulations (Promise/GOA) as a digital twin to evaluate policy alternatives under realistic order, inventory, and capacity patterns, including scenario and sensitivity analysis.
        \item Quantified projected impact of \$20M+ lower ship costs and \$300M+ incremental digital sales through improved conversion and margin.
        \item Implemented, tested, and tuned the algorithm under strict latency and reliability constraints for the P0 promise module.
        \item Influenced product, engineering, and fulfilment stakeholders via clear decision documents, presentations, and knowledge-transfer sessions to secure buy-in and plan roll-out.
    \end{itemize}
    }
    
    \cventry{\parbox[t]{2cm}{\raggedright 2023 -- \newline Present}}
    {Simulations Capability}{Target}{}{}{
      \begin{itemize}
        \item Led a 5-member team to design, implement, and maintain a unified simulation platform that acts as a digital twin for last-mile promise and fulfilment systems, now used by 100+ stakeholders across planning, digital fulfilment, and operations.
        \item Integrated Promise and GOA simulators into a single workflow enabling joint optimisation of delivery speed, node selection, and shipping cost for end-to-end scenarios.
        \item Transitioned data ingestion from static files to Kafka-based pipelines and scalable PySpark/Hive processing, improving data freshness and reducing manual intervention.
        \item Implemented robustness features such as input validation, scenario templates, and automated reporting, reducing user debug and support time by roughly 50\%.
        \item Owned roadmap and release management (three major and eight minor releases in 2025), including automated accuracy measurement and reporting frameworks.
    \end{itemize}
    }

    \cventry{\parbox[t]{2cm}{\raggedright 2024 -- \newline Present}}
    {Promise Simulator}{Target}{}{}{
    \begin{itemize}
        \item Developed an ATP simulator from scratch, covering algorithm design, data model, product discussions, interface design, and deployment automation.
        \item Ran large-scale backtests against production behaviour to validate the simulator and iteratively improve accuracy from about 40\% to 85\%, building trust with partner teams.
        \item Identified and delivered early use cases influencing roughly 3\% of all Target digital orders (\$600M+), including what-if analysis of promise policies and supply-chain strategies.
        \item Actively leveraged by fulfilment optimisation, engineering, and supply chain planning teams as the core platform for testing new promise and fulfilment logic before production rollout.
    \end{itemize}
    }

    \cventry{\parbox[t]{2cm}{\raggedright 2021 -- \newline 2024}}
    {Past Projects}{Target, WNS, IIMB, and Personal}{}{}{
    \noindent \textit{A list of selected past projects:}
    \href{https://github.com/nik141088/CV/blob/main/selected_past_projects_CV.pdf}{\texttt{selected\_past\_projects\_CV.pdf}}
    }


% \pagebreak


\hypertarget{tools-and-skills}{
\section{Tools and Skills}\label{tools-and-skills}}

\nopagebreak
    \cventry{\parbox[t]{2cm}{\raggedright Advanced}}{Programming \& Big Data}{Python, R, PySpark, Hive/SQL, Shiny/streamlit, C/C++, Kotlin/Java (basics)}{}{}{}
    \cventry{\parbox[t]{2cm}{\raggedright Advanced}}{Analytics \& Modelling}{Regression and classification, experiment design/A/B testing, NLP, feature engineering, MLOps (basics), h2o, TensorFlow/Keras}{}{}{}
    \cventry{\parbox[t]{2cm}{\raggedright Advanced}}{Design Principles}{Data structures and algorithms, computational/space complexity, vectorisation, functional programming, test-driven development, modular development, secure coding practices}{}{}{}
    \cventry{\parbox[t]{2cm}{\raggedright Advanced}}{Solutioning}{Problem solving, product thinking, scoping ambiguous problems, charting solutions, impact discovery, strategic thinking}{}{}{}
    \cventry{\parbox[t]{2cm}{\raggedright Advanced}}{Engineering \& Platforms}{APIs and services (plumber/fastapi), debugging, web scraping (selenium), Linux, code review, Git/GitHub, relational databases, Hadoop/Hive, Kafka, AWS, CI/CD}{}{}{}
    \cventry{\parbox[t]{2cm}{\raggedright Advanced}}{Visualisation \& Storytelling}{ggplot, plotly, R Markdown, Streamlit, dashboarding, LaTeX, MS Office; building clear narratives for technical and non-technical audiences}{}{}{}
    \cventry{\parbox[t]{2cm}{\raggedright Expert}}{Domain Knowledge}{Last-mile operations research (available-to-promise and order allocation), digital fulfilment and shipping cost optimisation, Finance, Accounting, Statistics, Regression analysis}{}{}{}
    \cventry{\parbox[t]{2cm}{\raggedright Progressive}}{Leadership}{Mentoring and coaching, project scoping/planning/managing, stakeholder management, product leadership, team building, hiring/interviewing}{}{}{}



\hypertarget{education}{
\section{Education}\label{education}}

\nopagebreak
    \cventry{\parbox[t]{2cm}{\raggedright 2016 -- \newline 2021}}
    {Doctor of Philosophy}{Finance and Accounting}{Indian Institute of Management, Bangalore}{}{CGPA: 3.64 / 4.00}
    \cventry{\parbox[t]{2cm}{\raggedright 2010 -- \newline 2012}}
    {Master of Engineering}{Electrical Communication Engineering}{Indian Institute of Science, Bangalore}{}{CGPA: 6.4 / 8.0; Project Grade: A}
    \cventry{\parbox[t]{2cm}{\raggedright 2006 -- \newline 2010}}
    {Bachelor of Technology}{Electronics and Communication Engg.}{Bundelkhand Institute of Engg. and Tech., Jhansi (U.P.)}{}{Grade: 73.6\%}
    \cventry{\parbox[t]{2cm}{\raggedright 2004 -- \newline 2006}}
    {Schooling (12th Standard)}{Science}{C.B.S.E.}{}{Grade: 88.2\%}

\hypertarget{awards-and-honors}{
\section{Awards and Honors}\label{awards-and-honors}}

\nopagebreak
    \cventry{\parbox[t]{2cm}{\raggedright 2022}}{Tech Genius, Transforming the Organization, Victory Fleet}{WNS Global Services}{}{}{}
    \cventry{\parbox[t]{2cm}{\raggedright 2020}}{Mirae Asset Scholarship (PhD Year 5)}{Indian Institute of Management}{}{}{}
    \cventry{\parbox[t]{2cm}{\raggedright 2017--2018}}{Director's Merit List (PhD Year 1 and 2)}{Indian Institute of Management}{}{}{}
    \cventry{\parbox[t]{2cm}{\raggedright 2016}}{96.5 percentile}{Common Aptitude Test (CAT)}{}{}{}
    \cventry{\parbox[t]{2cm}{\raggedright 2010}}{AIR 20/105,000}{Graduate Aptitude Test in Engineering (GATE)}{}{}{}
    \cventry{\parbox[t]{2cm}{\raggedright 2006--2007}}{Merit Scholarships}{Intermediate Examination and Engineering}{}{}{}



\end{document}

