---
# Help on how to format Rmarkdown CV can be found at: https://cran.r-project.org/web/packages/vitae/vignettes/vitae.html

name: Nikhil
surname: Vidhani
position: "Lead Data Scientist, Target Corporation"
profilepic: nikhil-wns-pic.jpg

phone: "+91-797-555-7296"
linkedin: "nikhil-vidhani"
email: nikhil141088@gmail.com
www: sites.google.com/view/nikhilvidhani
github: nik141088

headcolor: "A52A2A" # color of CV headings. More colors at: http://latexcolor.com/
date: "`r format(Sys.time(), '%B %Y')`"
# aboutme: About me! About me! About me! About me! About me! About me! About me! About me! About me! About me! About me! About me!
docname: Curriculum Vitae
header-includes:
    - \usepackage{ragged2e}
    - \usepackage{comment}
output:
  vitae::moderncv:
  # vitae::awesomecv:
  # vitae::hyndman:
    keep_tex: true
    theme: casual
    # theme: classic
    # theme: oldstyle
    # theme: banking
    # theme: fancy
csl: apa-cv.csl # change this if you want to use other citation styles
# bibliography_published: "published.bib" # use separate .bib files and assign each of them a unique key: bibliography_*
# bibliography_under_review: "under_review.bib"
# bibliography_working_paper: "working_paper.bib"
# bibliography_work_in_progress: "work_in_progress.bib"
# bibliography_presentations: "presentations.bib"
nocite: '@*' # don't change this if you want to print out all the refs
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae);

setwd("C:/Users/nikhi/Dropbox/research/CV_Nikhil_Vidhani_2023/");

# process yaml options
temp = readLines("CV_Nikhil_Vidhani_2023.Rmd");
idx = which(temp == "---"); # identify yaml portion of Rmd file
temp = temp[idx[1]:idx[2]];
yaml = yaml::yaml.load(temp);
```


\newenvironment{smallblockquote}{%
  \par%
  \medskip
  \leftskip=2em\rightskip=0em%
  \noindent\ignorespaces}{%
  \par\medskip}


\newenvironment{blockquote}{%
  \par%
  \medskip
  \leftskip=4em\rightskip=0em%
  \noindent\ignorespaces}{%
  \par\medskip}








# Executive Summary

\begingroup
\begin{blockquote}

I work as a Lead Data Scientist in the Digital Fulfillment team at Target Corporation. Our team builds digital supply chain simulation capability, which enables business teams to run what-if scenarios. I earlier worked with WNS Global Services, where I guided a team of data scientists in building data analytics apps in F\&A domain. I hold a Ph.D. in Finance and Accounting from IIM Bangalore and a masters from IISc Bangalore. I have presented my research at several prestigious international conferences. Besides, I have also trained hundreds of students and practitioners in R programming and data analysis.

\end{blockquote}
\endgroup









<!-- \newpage -->









# Industry, Research, and Teaching Experience

```{r}
library(tibble)
tribble(
  ~ job_title, ~ year, ~ company, ~ responsibilities,
  
  "Lead Data Scientist", "2022--", "Target Corporation, Bangalore",
  "Building supply chain simulation, available to promise (ATP), order allocation, big-data pipelines; code review",
  
  "Sr. Group Manager (Data Science)", "2022--2022", "WNS Global Services, Bangalore",
  "Building F&A apps in payments, collections, reporting, prediction, and auditing; Maintain codebase (github), APIs, deloyment automation; Conduct Knowledge-sharing Sessions",
  
  "Research Scholar", "2016--2022", "Indian Institute of Management, Bangalore",
  "Ideating research problem; identify data sources, collect/clean/transform data, model building (regression/ML/NLP); drafting research papers; presenting in conferences; https://github.com/nik141088",
  
  "Primary Instructor", "2018--2022", "R Programming; R Programming and Data Analysis; Introduction to Latex", "Training students and practitioners. Instructor Rating: 4.7/5. https://github.com/nik141088/applied-R",
  
  "Sr. Software Engineer", "2012--2016", "Cisco Systems, Bangalore",
  "Design, code, test, and documentation of 4G-LTE and WiFi nodes; High Availability/Redundancy architecture; Network security"
) %>% 
  detailed_entries(with = company, when = year, what = job_title, where = responsibilities)
```









<!-- \newpage -->









# Major Projects

```{r}
library(tibble)
tribble(
  ~place, ~title, ~details,
  
  "Target", "Promise Simulator",
  "Built available-to-promise (ATP) simulator from scratch. Enabled users to configure data sources, key algorithmic decisions to drive maximum usability across data-sciences, product, and business.",
  
  "Target", "Logging Infra",
  "Added logging infra in our in-house simulation capability to understand allocation level decisions. Built as a post-mortem tool to analyse previous simulation runs.",
  
  "WNS", "QA Analytics",
  "Highly configurable workflow tool designed to catch human errors in invoice indexing. Additionally, the tool provides a one-stop solution for outlier and anomalous transaction detection. Used by multiple auditors within WNS",
  
  "WNS", "Excel-API",
  "ML solution built with h2o framework and deployed through portable-R and plumber API. Helps controllers predict errors right from the comfort of excel",
  
  "WNS", "WNS Predictor",
  "A shiny application focused on democratizing machine learning by automating modeling and prediction for non data-scientists",

  "Personal", "Invoice Processing",
  "Deep Learning based tool to detect duplicate invoices. Comparison based on raw bytes, image, and OCR text. https://github.com/nik141088/invoice-processing",
  
  "IIMB", "Factiva Download",
  "Web-scrapping and article extraction project to study news sentiment and accounting behavior. https://github.com/nik141088/factiva-download",

) %>% 
  detailed_entries(when = place, what = title, where = details)
```









<!-- \newpage -->









# Tools and Skills

```{r}
library(tibble)
tribble(
  ~skill, ~level, ~details,
  
  "Data Science and Engineering",      "Expert", 
  "R, RStudio, Python, Shiny, debugging, data.table, computation",
  
  "Machine Learning and Big Data",                "Advanced", 
  "Regression, Classification, Decision Trees, NLP, h2o, pyspark, hadoop, SQL",
  
  "Programming", "Advanced", 
  "Algorithms, Data Structures, complexity, vectorization, C, Linux, security, OS, selenium",
  
  "Visualization and Documentation", "Advanced", 
  "ggplot, plotly, R Markdown, Latex, MS Office",
  
  "Domain Knowledge",                "Expert", 
  "Finance, Accounting, Statistics, Regression Analysis, Algorithms, Computation, R-Programming",
  
  "Deployment",                      "Advanced", 
  "github, AWS, Programmatic Access, API, Databases, git, CI/CD",
  
  "Management",                      "Progressive", 
  "Leadership, mentoring, project management"
  
) %>% 
  detailed_entries(what = skill, when = level, with = details)
```









<!-- \newpage -->









# Education

```{r}
library(tibble)
tribble(
  ~ Degree,
  ~ Course,
  ~ Year,
  ~ Institute,
  ~ Grade,
  
  "Doctor of Philosophy",
  "Finance and Accounting",
  "2016--2022",
  "Indian Institute of Management, Bangalore",
  "CGPA: 3.64 / 4.00",
  
  "Master of Engineering",
  "Electrical Communication Engineering",
  "2010--2012",
  "Indian Institute of Science, Bangalore",
  "CGPA: 6.4 / 8.0; Project Grade: A",
  
  "Bachelor of Technology",
  "Electronics and Communication Engg.",
  "2006--2010",
  "Bundelkhand Institute of Engg. and Tech., Jhansi (U.P.)",
  "73.6 %",
  
  "Schooling (12th Standard)",
  "Science",
  "2004--2006",
  "C.B.S.E.",
  "88.2 %",
) %>% 
  detailed_entries(what = Degree, when = Year, with = Course, where = Institute, why = Grade)
```









<!-- \newpage -->









# Awards and Honors


```{r}
tribble(
  ~Year, ~Award, ~Institution,
  "2022", "Tech Genius, Transforming the Organization, Victory Fleet", "WNS Global Services",
  "2020", "Mirae Asset Scholarship (PhD Year 5)", "Indian Institute of Management",
  "2017--2018", "Director's Merit List (PhD Year 1 and 2)", "Indian Institute of Management",
  "2016", "96.5 percentile", "Common Aptitute Test (CAT)",
  "2010", "All India Rank 20 out of 105,000 participants", "Graduate Aptitude Test in Engineering (GATE)",
  "2006--2007", "Merit Scholarships", "Intermediate Examination and Engineering",
) %>% 
  detailed_entries(what = Award, with = Institution, when = Year)
```









\newpage









# Publications 

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\begin{smallblockquote}
Sunny, A., Panchal, S., \textbf{Vidhani, N.}, Krishnasamy, S., Anand, S., Hegde, M., Kuri, J., \& Kumar, A. (2017). \textbf{\textit{A generic controller for managing TCP transfers in IEEE 802.11 infrastructure WLANs}}. Journal of Network and Computer Applications, Vol 93, pp 13--26. \underline{DOI:} \url{https://doi.org/10.1016/j.jnca.2017.05.006}.\\
\textbf{Impact Factor:} 6.28\\
\end{smallblockquote}


\begin{smallblockquote}
\textbf{Vidhani, N.}, (2022). \textbf{\textit{Return Predictability using
Price-to-Earnings Ratio}}. \underline{SSRN:} \url{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3910641}.\\
\textbf{Revise and Resubmit:} Journal of Forecasting, ABDC-A\\
\textbf{Impact Factor:} 2.31\\
\textbf{Conferences:} \textit{International Conference on Derivatives and Capital Markets (ICDCM-2021)\textsuperscript{\#}, World Finance and Banking Symposium (WFBS-2021)\textsuperscript{\#}, India Finance Conference (IFC-2021)\textsuperscript{\#}, 15th NYCU International Finance Conference (2021)\textsuperscript{\#}, Asian Management Research and Case Conference (2022)\textsuperscript{\#}}\\
\textit{\textsuperscript{\#} selected but not presented}\\
\end{smallblockquote}


\begin{smallblockquote}
\textbf{Vidhani, N.}, (2022). \textbf{\textit{Trading Volume and Dispersion of Signals}}. \underline{SSRN:} \url{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3682088}.\\
\textbf{Submission Journal:} The Journal of Finance, FT50\\
\textbf{Conferences:} \textit{International Conference on Derivatives and Capital Markets (ICDCM-2020), International Risk Management Conference (IRMC-2020), Southern Finance Association (SFA-2020), Conference on Asia-Pacific Financial Markets (CAFM-2020) Doctoral Consortium, World Finance and Banking Symposium (WFBS-2020), Theories and Practices of Securities and Financial Markets (SFM-2020), 12th Emerging Market Finance Conference (2020), Southwestern Finance Association (SWFA-2021), International Conference of the French Finance Association (AFFI-2021), IIM Bangalore}\\
\end{smallblockquote}


\begin{smallblockquote}
Krishnan, M., Rangan, S., \& \textbf{Vidhani, N.}, (2021). \textbf{\textit{Pricing of Earnings in the Presence of Informed Trades: A Simple GMM Approach}}. \underline{SSRN:} \url{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3560147}.\\
\textbf{Under Review:} Review of Economics and Statistics, ABDC-A\textsuperscript{\textasteriskcentered}\\
\textbf{Conferences:} \textit{2015 NSE-NYU Conference\textsuperscript{\#}, CAFRAL at RBI\textsuperscript{\#}, IIM-Calcutta Finance Research Workshop\textsuperscript{\#}, 3rd JAAF-India Conference\textsuperscript{\#}, IIM Bangalore\textsuperscript{\#}, IIT-Madras\textsuperscript{\#}, IIT-Kharagpur\textsuperscript{\#}, University of Washington\textsuperscript{\#}}\\
\textit{\textsuperscript{\#} presented by co-authors}\\
\end{smallblockquote}

\endgroup












