---
# Help on how to format Rmarkdown CV can be found at: https://cran.r-project.org/web/packages/vitae/vignettes/vitae.html

name: Nikhil
surname: Vidhani
position: "Sr. Group Manager (Data Science), WNS Global Services"
profilepic: nikhil-wns-pic.jpg

phone: "+91-797-555-7296"
linkedin: "nikhil-vidhani"
email: nikhil141088@gmail.com
www: sites.google.com/view/nikhilvidhani
github: nik141088

headcolor: "A52A2A" # color of CV headings. More colors at: http://latexcolor.com/
date: "`r format(Sys.time(), '%B %Y')`"
# aboutme: About me! About me! About me! About me! About me! About me! About me! About me! About me! About me! About me! About me!
docname: Curriculum Vitae
header-includes:
    - \usepackage{ragged2e}
    - \usepackage{comment}
output:
  vitae::moderncv:
  # vitae::awesomecv:
  # vitae::hyndman:
    keep_tex: true
    theme: casual
    # theme: classic
    # theme: oldstyle
    # theme: banking
    # theme: fancy
csl: apa-cv.csl # change this if you want to use other citation styles
# bibliography_published: "published.bib" # use separate .bib files and assign each of them a unique key: bibliography_*
# bibliography_under_review: "under_review.bib"
# bibliography_working_paper: "working_paper.bib"
# bibliography_work_in_progress: "work_in_progress.bib"
# bibliography_presentations: "presentations.bib"
nocite: '@*' # don't change this if you want to print out all the refs
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae);

setwd("C:/Users/nikhi/Dropbox/GitHub/CV/");

# process yaml options
temp = readLines("CV_Nikhil_Vidhani_2022.Rmd");
idx = which(temp == "---"); # identify yaml portion of Rmd file
temp = temp[idx[1]:idx[2]];
yaml = yaml::yaml.load(temp);
```


\newenvironment{smallblockquote}{%
  \par%
  \medskip
  \leftskip=2em\rightskip=0em%
  \noindent\ignorespaces}{%
  \par\medskip}


\newenvironment{blockquote}{%
  \par%
  \medskip
  \leftskip=4em\rightskip=0em%
  \noindent\ignorespaces}{%
  \par\medskip}








# Executive Summary

\begingroup
\begin{blockquote}

Nikhil Vidhani works as a senior group manager in the F\&A capability at WNS. He guides a team of data scientists in building data analytics apps. He holds a Ph.D. in Finance and Accounting from IIM Bangalore, where he has provided research consultancy and training in data analytics. His work revolves around predicting financial variables. He also handles software development tasks like version control, integration, and deployment. Earlier in his career, he worked with Cisco Systems as a senior software engineer.\\
\\
In his dissertation, Nikhil has explored the return predictability literature in great depth. He proposed a new measure of investor disagreement based on return anomalies and linked this to forecasting stock volume. He has presented his research at several prestigious international conferences across the globe. Besides, Nikhil has also trained hundreds of students and practitioners at IIM Bangalore in R programming, data analysis, and freelanced research projects for colleagues within and outside IIM Bangalore.

\end{blockquote}
\endgroup









# Education

```{r}
library(tibble)
tribble(
  ~ Degree,
  ~ Course,
  ~ Year,
  ~ Institute,
  ~ Grade,
  
  "Doctor of Philosophy",
  "Finance and Accounting",
  "2016--2022",
  "Indian Institute of Management, Bangalore",
  "CGPA: 3.64 / 4.00",
  
  "Master of Engineering",
  "Electrical Communication Engineering",
  "2010--2012",
  "Indian Institute of Science, Bangalore",
  "CGPA: 6.4 / 8.0; Project Grade: A",
  
  "Bachelor of Technology",
  "Electronics and Communication Engg.",
  "2006--2010",
  "Bundelkhand Institute of Engg. and Tech., Jhansi (U.P.)",
  "73.6 %",
  
  "Intermediate (12th Standard)",
  "Science",
  "2006",
  "C.B.S.E.",
  "88.2 %",

  "High School (10th Standard)",
  "",
  "2004",
  "C.B.S.E.",
  "81.6 %",
) %>% 
  detailed_entries(what = Degree, when = Year, with = Course, where = Institute, why = Grade)
```













\newpage
# Industry, Research, and Teaching Experience

```{r}
library(tibble)
tribble(
  ~ job_title, ~ year, ~ company, ~ responsibilities,
  
  "Sr. Group Manager (Data Science)", "2022--", "WNS Global Services, Bangalore", "Building F&A apps in payments, collections, reporting, prediction, and auditing; Maintain codebase (github), APIs, deloyment automation; Conduct Knowledge-sharing Sessions",
  
  "Research Consultant", "2016--2022", "Indian Institute of Management, Bangalore", "Ideating research problem; identify data sources, collect/clean/transform data, model building (regression/ML/NLP); drafting research papers; presenting in conferences",
  
  "Primary Instructor", "2018--2022", "R Programming; R Programming and Data Analysis; Introduction to Latex", "Training students and practitioners. Instructor Rating: 4.7/5",
  
  "Sr. Software Engineer", "2012--2016", "Cisco Systems, Bangalore", "Design, code, test, and documentation of 4G-LTE and WiFi nodes; High Availability/Redundancy architecture; Network security",
) %>% 
  detailed_entries(with = company, when = year, what = job_title, where = responsibilities)
```

















# Tools and Skills

```{r}
library(tibble)
tribble(
  ~skill, ~level, ~details,
  
  "Data Science and Analytics", "Expert", "R, RStudio, Python, Shiny, debugging, machine learning, NLP, data.table, computation, selenium",
  
  "Programming", "Expert", "Algorithms, Data Structures, C, Linux, R, Shiny (reactivity), Python, security, OS",
  
  "Visualization and Documentation", "Advanced", "ggplot, plotly, R Markdown, Latex, MS Office",
  
  "Domain Knowledge", "Expert", "Finance, Accounting, Statistics, Algorithms, Computation, R-Programming",
  
  "Deployment", "Advanced", "github, AWS, Programmatic Access, API, Databases, SQL, git, CI/CD",
  
  "Management", "Progressive", "Leadership, mentoring, project management"
  
) %>% 
  detailed_entries(what = skill, when = level, with = details)
```











\newpage
# Awards and Honors

```{r}
tribble(
  ~Year, ~Award, ~Institution,
  2020, "Mirae Asset Scholarship (PhD Year 5)", "Indian Institute of Management",
  2018, "Director's Merit List (PhD Year 2)", "Indian Institute of Management",
  2017, "Director's Merit List (PhD Year 1)", "Indian Institute of Management",
  2016, "96.5 percentile", "Common Aptitute Test (CAT)",
  2010, "Ministry of HRD Scholarship (2 years)", "Indian Institute of Science",
  2010, "All India Rank 20 out of 105,000 participants", "Graduate Aptitude Test in Engineering (GATE)",
  2007, "Merit Scholarship (top 10 students across institute)", "Bundelkhand Institute of Engg. and Tech.",
  2006, "All India Rank 1045 out of 300,000 participants", "Uttar Pradesh State Entrance Exam (SEE-UPTU)",
  2006, "Among top 10 students from Agra city", "Intermediate Examination",
) %>% 
  detailed_entries(what = Award, with = Institution, when = Year)
```









# Publications 

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\begin{smallblockquote}
Sunny, A., Panchal, S., \textbf{Vidhani, N.}, Krishnasamy, S., Anand, S., Hegde, M., Kuri, J., \& Kumar, A. (2017). \textbf{\textit{A generic controller for managing TCP transfers in IEEE 802.11 infrastructure WLANs}}. Journal of Network and Computer Applications, Vol 93, pp 13--26. \underline{DOI:} \url{https://doi.org/10.1016/j.jnca.2017.05.006}.\\
\textbf{Impact Factor:} 6.28\\
\end{smallblockquote}


\begin{smallblockquote}
\textbf{Vidhani, N.}, (2021). \textbf{\textit{Return Predictability using
Price-to-Earnings Ratio}}. \underline{SSRN:} \url{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3910641}.\\
\textbf{Revise and Resubmit:} Journal of Forecasting, ABDC-A\\
\textbf{Impact Factor:} 2.31\\
\textbf{Conferences:} \textit{International Conference on Derivatives and Capital Markets (ICDCM-2021)\textsuperscript{\#}, World Finance and Banking Symposium (WFBS-2021)\textsuperscript{\#}, India Finance Conference (IFC-2021)\textsuperscript{\#}, 15th NYCU International Finance Conference (2021)\textsuperscript{\#}}\\
\textit{\textsuperscript{\#} selected but not presented}\\
\end{smallblockquote}

\begin{smallblockquote}
\textbf{Vidhani, N.}, (2021). \textbf{\textit{Trading Volume and Dispersion of Signals}}. \underline{SSRN:} \url{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3682088}.\\
\textbf{Submission Journal:} The Journal of Finance, FT50\\
\textbf{Conferences:} \textit{International Conference on Derivatives and Capital Markets (ICDCM-2020), International Risk Management Conference (IRMC-2020), Southern Finance Association (SFA-2020), Conference on Asia-Pacific Financial Markets (CAFM-2020) Doctoral Consortium, World Finance and Banking Symposium (WFBS-2020), Theories and Practices of Securities and Financial Markets (SFM-2020), 12th Emerging Market Finance Conference (2020), Southwestern Finance Association (SWFA-2021), International Conference of the French Finance Association (AFFI-2021), IIM Bangalore}\\
\end{smallblockquote}

\begin{smallblockquote}
Krishnan, M., Rangan, S., \& \textbf{Vidhani, N.}, (2021). \textbf{\textit{Pricing of Earnings in the Presence of Informed Trades: A Simple GMM Approach}}. \underline{SSRN:} \url{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3560147}.\\
\textbf{Under Review:} Review of Economics and Statistics, ABDC-A\textsuperscript{\textasteriskcentered}\\
\textbf{Conferences:} \textit{2015 NSE-NYU Conference\textsuperscript{\#}, CAFRAL at RBI\textsuperscript{\#}, IIM-Calcutta Finance Research Workshop\textsuperscript{\#}, 3rd JAAF-India Conference\textsuperscript{\#}, IIM Bangalore\textsuperscript{\#}, IIT-Madras\textsuperscript{\#}, IIT-Kharagpur\textsuperscript{\#}, University of Washington\textsuperscript{\#}}\\
\textit{\textsuperscript{\#} presented by co-authors}\\
\end{smallblockquote}

\begin{smallblockquote}
Rangan, S., \& \textbf{Vidhani, N.}, (2021). \textbf{\textit{New Evidence on Accounting Conservatism}}.\\
\textbf{Work-In-Progress}\\
\end{smallblockquote}

\endgroup












# Datasets

\begingroup
\begin{blockquote}

CRSP, Compustat Capital IQ, IBES, Wharton Research Data Services (WRDS) databases, CMIE Prowess-dx, NSE Trade/Order book, Bloomberg Terminal, Thomson Reuters Eikon, Factiva News database, Twitter, SEC EDGAR, Calcbench.

\end{blockquote}
\endgroup













# Conference Presentations

```{r}
tribble(
  ~Year, ~Conference, ~Place,
  "May 2021", "International Conference of the French Finance Association (AFFI)", "Audencia Business School, France",
  "Mar 2021", "Southwestern Finance Association (SWFA)", "",
  "Dec 2020", "11th Emerging Market Finance Conference", "Finance Research Group, Mumbai",
  "Dec 2020", "Theories and Practices of Securities and Financial Markets (SFM)", "National Sun Yat-sen University, Taiwan",
  "Dec 2020", "World Finance and Banking Symposium", "University of Latvia, Latvia",
  "Dec 2020", "15th Conference on Asia-Pacific Financial Markets (CAFM)", "Korean Securities Association, Seoul, Korea",
  "Nov 2020", "Southern Finance Association (SFA)", "Palm Springs, California, USA",
  "Oct 2020", "International Risk Management Conference (IRMC)", "The Risk Society, Italy",
  "Aug 2020", "International Conference on Derivatives and Capital Markets (ICDCM)", "Shandong University, China",
  "Sep 2019", "Talk given to finance group at IIM, Bangalore", "IIM Bangalore",
) %>% 
  detailed_entries(what = Conference, when = Year, with = Place)
```











# References

```{r}
tribble(
  ~name, ~title, ~contact,
  "Srinivasan Rangan",  "Associate Professor, Indian Institute of Management, Bangalore", "srinivasanr@iimb.ac.in",
  "Anand Sasidharan",  "Director, WNS Global Services, Bangalore", "2anandsasi@gmail.com",
  "Murugappa Krishnan",  "Professor, University of Washington, Bothell", "murgie@uw.edu",
) %>% 
  detailed_entries(what = name, where = title, with = contact)
```






